### 2015-03-11 article/article.tex
commit

	\textbf{Strain} & \textbf{Gene}  & \textbf{Feature} & \textbf{Phenotype} & \textbf{Z-score}

@@

	CAST/EiJ  & Rora (RAR-related orphan receptor alpha) & protein coding gene & trigonelline relative abundance &  8.8 \\
	C58/J  & Rorc (RAR-related orphan receptor gamma) & protein coding gene & N-acetylglutamate relative abundance & 8.4\\ 
	CAST/EiJ  & Rara (retinoic acid receptor, alpha) & protein coding gene & N2-acetyllysine (16h fast), relative abundance &  4.6\\ 
	NZB/BlNJ & Nr1i3 (nuclear receptor subfamily 1, group I, member 3) & protein coding gene & ECG parameters interval between peak of P-wave to R-wave (PR) &  4.6\\ 
	CE/J & Nr0b1 (nuclear receptor subfamily 0, group B, member 1) & protein coding gene & kidney total weight &  4.4\\
	NZB/BlNJ  & Nr5a1 (nuclear receptor subfamily 5, group A, member 1) & protein coding gene & succinylcarnitine relative abundance  &  3.8\\
	C57L/J & Esr2 (estrogen receptor 2 beta) & protein coding gene & 

@@

	NOD/ShiLtJ  & Ppard (peroxisome proliferator activator receptor delta)  & protein coding gene & 

@@

	BUB/BnJ & Esr1 (estrogen receptor 1 alpha) & protein coding gene & 3-dehydrocarnitine  relative abundance &  2.7\\  

>>>>

	\textbf{Strain} & \textbf{Gene}  & \textbf{Phenotype} & \textbf{Z-score}

@@

	CAST/EiJ  & Rora (RAR-related orphan receptor alpha) & trigonelline relative abundance &  8.8 \\
	C58/J  & Rorc (RAR-related orphan receptor gamma) & N-acetylglutamate relative abundance & 8.4\\ 
	CAST/EiJ  & Rara (retinoic acid receptor, alpha) & N2-acetyllysine (16h fast), relative abundance &  4.6\\ 
	NZB/BlNJ & Nr1i3 (nuclear receptor subfamily 1, group I, member 3) & ECG parameters interval between peak of P-wave to R-wave (PR) &  4.6\\ 
	CE/J & Nr0b1 (nuclear receptor subfamily 0, group B, member 1) & kidney total weight &  4.4\\
	NZB/BlNJ  & Nr5a1 (nuclear receptor subfamily 5, group A, member 1) & succinylcarnitine relative abundance  &  3.8\\
	C57L/J & Esr2 (estrogen receptor 2 beta) & 

@@

	NOD/ShiLtJ  & Ppard (peroxisome proliferator activator receptor delta) & 

@@

	BUB/BnJ & Esr1 (estrogen receptor 1 alpha) & 3-dehydrocarnitine  relative abundance &  2.7\\  
